Dirac neutrino mass generation from Majorana messenger

### 2019-09-14 draft.tex
lc

\section{Collider constraints}
The recasting of the latest ATLAS results for the search of dilepton resonances using $139\ \text{fb}^{-1}$~\cite{1903.06248} was done
in~\cite{1903.06248} for the $\operatorname{U}(1)_{B-L}$ model.
The green region in Fig.~\ref{fig:u1blc} shows the excluded region at $95\%\ \text{C.L.}$. To ease the comparison with other results, we show the exclusion as function of $M_{Z'}/g_{BL}$. In particular, the limit from LEP for $\operatorname{U}(1)_{B-L}$ model is~\cite{1408.6845}, 
\begin{align}
  M_{Z'}/g_{BL}>6.7\ \text{TeV}\,,&&\text{at $95\%$ C.L }
\end{align}

>>>>

\section{Collider constraints}
The recasting of the latest ATLAS results for the search of dilepton resonances using $139\ \text{fb}^{-1}$~\cite{Aad:2019fac} was done
in~\cite{Aad:2019fac} for the $\operatorname{U}(1)_{B-L}$ model.
The green region in Fig.~\ref{fig:u1blc} shows the excluded region at $95\%\ \text{C.L.}$. To ease the comparison with other results, we show the exclusion as function of $M_{Z'}/g_{BL}$. In particular, the limit from LEP for $\operatorname{U}(1)_{B-L}$ model is~\cite{Heeck:2014zfa}, 
\begin{align}
  M_{Z'}/g_{BL}>6.7\ \text{TeV}\,,&&\text{at $95\%$ C.L }
\end{align}
